TGI-spinal-power

### 2022-05-20 analysis/tgispine_zoib_power-sim.Rmd
tidying up sim file, more logical order

# setting working directory
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
knitr::opts_knit$set(root.dir = datPath)
```

@@

return(summary(mod))}
```

# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for this model only
# do this for 40 participants, for 1000 simulations
nSims <- 500
n <- 32 # number of participants to simulate
po <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i, 0, 1)
    df_sim <- rbind(df_sim,df)
    }
  # then run the model based on simulated data
  m <- model(df_sim, 'cold')
  # extracting the p-value and effect size
  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
  po <- rbind(po,tmp)
}

@@

# Then warm
```{r}
# the warm model has the smallest effect size, so should extract power calculation for this model only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i, 0, 1)
    df_sim <- rbind(df_sim,df)
    }
  # then run the model based on simulated data
  m <- model(df_sim, 'warm')
  # extracting the p-value and effect size
  tmp <- c(m$coefficients$cond[4,4], m$coefficients$cond[4,1])
  po <- rbind(po,tmp)
}

@@

# Plotting data distributions to see what kind of model family is required
```{r}
# do this for the largest simulated dataset
df40$quality <- factor(df40$quality, 
                             levels = c("cold", "warm", "burn"))
ggplot2::ggplot(data = df40) +
  geom_density(aes(rating, fill = stimuli), alpha = .5) +
  facet_wrap(~quality) +
  theme_classic()
```

# Now plot most recently simulated data
# Summary statistics for the largest data set - for plotting
```{r}
# define each condition
df40$conditionN[df40$dermatome == "within" & df40$cold_location == "dist_rostr"] <- 1
df40$conditionN[df40$dermatome == "within" & df40$cold_location == "prox_caud"] <- 2
df40$conditionN[df40$dermatome == "across" & df40$cold_location == "dist_rostr"] <- 3
df40$conditionN[df40$dermatome == "across" & df40$cold_location == "prox_caud"] <- 4

@@

# Look at model assumptions
```{r}
# cold assumption - on n = 20
model.cold.assmup <- simulateResiduals(model.cold40, n = 1000)
plot(model.cold.assmup)
```

>>>>

# setting working directory
datPath <- '/home/alexm/sTGI/'
knitr::opts_knit$set(root.dir = datPath)
```

@@

return(mod)}
```

# First, simulate one data-set and run models (warm, cold and burn perception) to take a look at data
```{r}
df_sim <- data.frame()
n = 50 #an example number of participants
for (i in 1:n) {
  df <- simulate_subj(i, 0, 1)
  df_sim <- rbind(df_sim,df)
}
df50 <- df_sim

# Plotting data distributions to see what kind of model family is required
df50$quality <- factor(df50$quality, 
                             levels = c("cold", "warm", "burn"))
ggplot2::ggplot(data = df50) +
  geom_density(aes(rating, fill = stimuli), alpha = .5) +
  facet_wrap(~quality) +
  theme_classic()
```

# running models based on simmed data
```{r}
# models for each VAS
mc <- model(df_sim, 'cold')
mw <- model(df_sim, 'warm')
mb <- model(df_sim, 'burn')

# show models
summary(mc)
summary(mw)
summary(mb)
```

# Look at model assumptions
```{r}
# cold assumption - on n = 50
mc.assump <- simulateResiduals(mc, n = 1000)
plot(mc.assump)
```

## SIMULATIONS ##
# Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model
# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for this model only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 40 # number of participants to simulate
po <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i, 0, 1)
    df_sim <- rbind(df_sim,df)
    }
  # then run the model based on simulated data
  m <- model(df_sim, 'cold')
  m1 <- summary(m)
  # extracting the p-value and effect size
  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
  po <- rbind(po,tmp)
}

@@

# Then warm
```{r}
# the warm model has the smallest effect size, so should extract power calculation for this model only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i, 0, 1)
    df_sim <- rbind(df_sim,df)
    }
  # then run the model based on simulated data
  m <- model(df_sim, 'warm')
  m1 <- summary(m)
  # extracting the p-value and effect size
  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
  po <- rbind(po,tmp)
}

@@

## PLOTTING - plot simulated data (d50 from earlier)
# Summary statistics for the largest data set - for plotting
```{r}
# define each condition
df50$conditionN[df50$dermatome == "within" & df50$cold_location == "dist_rostr"] <- 1
df50$conditionN[df50$dermatome == "within" & df50$cold_location == "prox_caud"] <- 2
df50$conditionN[df50$dermatome == "across" & df50$cold_location == "dist_rostr"] <- 3
df50$conditionN[df50$dermatome == "across" & df50$cold_location == "prox_caud"] <- 4

@@
